Title

### 2021-03-04 Papers/02_Sound_Compression/SoundRepresentation.tex
working char in disk implementation

The first format we compare to is the popular MP3, the third layer of MPEG-1/2 specification, proposed in 1992 \parencite{2018BritanakAudio}. Despite being superseeded by the newer MPEG-2 AAC \parencite{1999BrandenburgMP3}, finalized five years later, which we also compare, its ubiquity makes the comparison crucial.

>>>>

The first format we compare to is the popular MP3, the third layer of MPEG-1/2 specification, proposed in 1992 \parencite{2018BritanakAudio}. Despite being technically superseded by the newer MPEG-2 AAC \parencite{1999BrandenburgMP3}, finalized five years later, with which we also compare, its ubiquity makes the comparison crucial.
